Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-15 presentations/bsa_2020-07-27/index.Rmd
Update slides

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
output:
  xaringan::moon_reader:
    css: ["default-fonts", "default", "custom.css"]
    lib_dir: libs
    mathjax: default
    seal: false
    nature:
      slideNumberFormat: "" # To turn off slide numbers
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      titleSlideClass: ["left", "middle", "inverse"]
editor_options:
  chunk_output_type: console
---

>>>>

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
output:
  xaringan::moon_reader:
    css: ["default-fonts", "default", "custom.css"]
    lib_dir: libs
    mathjax: default
    seal: false
    nature:
      # slideNumberFormat: "" # To turn off slide numbers
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      titleSlideClass: ["left", "middle", "inverse"]
editor_options:
  chunk_output_type: console
---
